Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-25 writeup/parkinsons.tex
Initial affinity propagation
Next step - interpreting the results of the 8 clusters and seeing if
they mesh with the 4 k-means clusters

>>>>

\section{Affinity Propagation}

\subsection{Clustering}

AP with input preferences minimized ($q = 0$) resulted in 8 clusters.
With the standard median input preferences ($q = 0.5$), algorithm failed to
converge with default parameters. Even setting damping factor to 0.98, maximum
iterations to 10000, and convergence iterations to 1000 failed to converge.
Might need to try a longer term work.

\emph{However}, given that input preferences control how many clusters are
found, I don't think it's very useful to have some dozen clusters running
around.

\subsubsection{Silhouette Plots}

Silhouette plot in Figure~\ref{fig:ap-silhouette} looks pretty weak, really.
Tons of overlap between the clusters.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{ap-silhouette.pdf}
  \caption{AP silhouette plot, $k = 8$}
  \label{fig:ap-silhouette}
\end{figure}

\subsection{Interpretation}

Boxplot summary of clusters available in Figure~\ref{fig:ap-summaries}.
\textbf{Discussion forthcoming.}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{ap-summaries.pdf}
  \caption{AP Boxplot Summaries}
  \label{fig:ap-summaries}
\end{figure}
